Dynein project log

### 2016-12-22 thesis_stuff/thesis_stuff.tex
Minor change to preexponential factor thesis_stuff.pdf calc.
Fix previous fix of thesis_stuff.pdf.
Add work on [ATP] from Weihong's paper.

>>>>

\subsection{ATP Concentration from Weihong's Paper}
Weihong says in the Supplemental Methods section that the ATP concentration of the ``dynein motility buffer'' used to take his videos was 1mM, with no added ADP or Pi. Thus we need to calculate the equilibrium concentration of ATP:\\

\begin{align*}
  \Delta G^\cdot' &= \Delta G^\cdot + RT\ln Q\\
  \rightarrow Q &= e^{-\frac{\Delta G^\cdot}{RT}}\\
  \frac{[ADP][Pi]}{[ATP]} = \frac{n^2}{0.001 - n} &= e^{\frac{30.5}{0.008134*298}} = 2.915 * 10^{5}\\
  \rightarrow n \approx 0.001
\end{align*}

Thus we see that $[ADP] = [Pi] \approx 0.001$, $[ATP] = 3.4*10^{-12}$. What's more, we see that, since the [ATP] and [ADP] are at equilibrium, there is no energy to be gained
from hydrolysing ATP. Thus, dynein can't move. Maybe something is wrong...\\
